### 2013-08-21 exact_learning/paper.tex
make tables more consistent
Add inferred dimensions to the itm paper...
remove all occurences of i.e. and e.g. minor fixes

Let $o_{\W}(\theta)$ denote objective \eqref{oneslack} with
given parameters $\theta$ restricted to a working set $\W$, as computed in
line~\ref{restricted} of Algorithm~\ref{alg_cutting_plane} and  let
\[
    o^I(\theta) = C\xi' + \frac{||\theta||}{2}^2
\]
when using inference algorithm $I$, i.e. $o^I(\theta)$ is the approximation of the primal
objective given by $I$. To simplify exposure, we will drop the dependency on $\theta$.

Depending on the properties of the inference procedure $I$ used, it is easy to see:
\begin{enumerate}
    \item If all constraints $\hat{y}$ in  $\W$ are feasible, i.e.\ generated
        by an under-generating or exact inference mechanism, then $o_{\W}$ is
        an lower bound on the true optimum $o(\theta^*)$.

@@

We can also use these observations to judge the suboptimality of a given parameter $\theta$,
i.e.\ see how far the current objective is from the true optimum.
Learning with any under-generating approach, we can use 1. to maintain a lower bound
on the objective. At any point during learning, in particular if no more constraints
can be found, we can then use 2., to also find an upper bound.
This way, we can empirically bound the estimation error, using only approximate
inference.
We will now describe how we can further use 1. to both speed up and improve learning.

@@

%More precisely, let $o_{\W}(\theta)$ denote objective \eqref{oneslack} with
%given parameters $\theta$ restricted to a working set $\W$, as computed in
%line~\ref{restricted} of Algorithm~\ref{alg_cutting_plane} and  let
%\[
    %o^I(\theta) = C\xi' + \frac{||\theta||}{2}^2
    %\]
%when using inference algorithm $I$, i.e. $o^I(\theta)$ is the approximation of the primal
%objective given by $I$. To simplify exposure, we will drop the dependency on $\theta$.
In the following, we will use the notation of Section~\ref{bounds} and indicate
the choices of oracle $I$ with $Q$ for a chosen inference algorithm and $C$ for
using cached constraints.

@@

\begin{table}
    \begin{center}
    \begin{tabular}{lcc}
        \toprule
                    & Average & Global \\
        \cmidrule{1-3}
    Unary terms only & 77.7& 83.2 \\
    Pairwise model (move making)& 79.6&84.6\\
    Pairwise model (exact)& 79.0 & 84.3\\
        \cmidrule{1-3}
    \citet{ladicky2009associative} & 75.8& 85.0\\
    \citet{gonfaus2010harmony} & 77&  75\\
    \citet{lucchi2013learning} & 78.9& 83.7\\
    \bottomrule
    \end{tabular}
    \end{center}
    \caption{Accuracies on the MSRC-21 Dataset.  We compare a baseline model,
    our exact and approximately learned models and state-of-the-art
    approaches.\label{msrcacc}}

@@

\begin{figure*}
\centering
\includegraphics[width=.7\linewidth]{caching}
\caption{%
Training time comparison using different caching heuristics.
Large dots correspond to $o^Q$, small dots correspond to $o^C$,
and the line shows $o_\W$. See the text for details.\label{caching}}
\end{figure*}
% much simpler model?

@@

\begin{table}
    \begin{center}
    \begin{tabular}{lc}
        \toprule
                    & Jaccard \\
        \cmidrule{1-2}
    Unary terms only &  27.5 \\
    Pairwise model (move making)& 30.2\\
    Pairwise model (exact) & 30.4\\
        \cmidrule{1-2}
    \citet{dann2012pottics} & 27.4\\
    \citet{krahenbuhl2012efficient} & 30.2\\
    \citet{krahenbuhlparameter} & 30.8\\
    \bottomrule
    \end{tabular}
    \end{center}
    \caption{Accuracies on the Pascal VOC Dataset. We compare our approach
    against approaches using the same unary potentials.\label{pascalacc}}

@@

\begin{table}
    \begin{center}
    \begin{tabular}{lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ & 65.10 & 67.66  \\
    Estimated Objective $o^I$ &  67.62& 67.66\\
    True Primal Objective $o^E$& 69.92& 67.66\\
    \bottomrule
    \end{tabular}
    \end{center}
    \caption{Objective function values on the MSRC-21 Dataset}
    \label{msrc_objective}
\end{table}

@@

\begin{table}
    \begin{center}
    \begin{tabular}{lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ &92.06& 92.24\\
    Estimated Objective $o^I$ & 92.07 &92.24\\
    True Primal Objective $o^E$&92.35& 92.24  \\
    \bottomrule
    \end{tabular}
    \end{center}
    \caption{Objective function values on the Pascal Dataset.}
    \label{pascal_objective}
\end{table}

>>>>

Let $o_{\W}(\theta)$ denote objective \eqref{oneslack} with
given parameters $\theta$ restricted to a working set $\W$, as computed in
line~\ref{restricted} of Algorithm~\ref{alg_cutting_plane} and  let
\[
    o^I(\theta) = C\xi' + \frac{||\theta||}{2}^2
\]
when using inference algorithm $I$, that is $o^I(\theta)$ is the approximation of the primal
objective given by $I$. To simplify exposure, we will drop the dependency on $\theta$.

Depending on the properties of the inference procedure $I$ used, it is easy to see:
\begin{enumerate}
    \item If all constraints $\hat{y}$ in  $\W$ are feasible, that is generated
        by an under-generating or exact inference mechanism, then $o_{\W}$ is
        an lower bound on the true optimum $o(\theta^*)$.

@@

We can also use these observations to judge the suboptimality of a given parameter $\theta$,
that is see how far the current objective is from the true optimum.
Learning with any under-generating approach, we can use 1. to maintain a lower bound
on the objective. At any point during learning, in particular if no more constraints
can be found, we can then use 2., to also find an upper bound.
This way, we can empirically bound the estimation error, using only approximate
inference.
We will now describe how we can further use 1. to both speed up and improve learning.

@@

%More precisely, let $o_{\W}(\theta)$ denote objective \eqref{oneslack} with
%given parameters $\theta$ restricted to a working set $\W$, as computed in
%line~\ref{restricted} of Algorithm~\ref{alg_cutting_plane} and  let
%\[
    %o^I(\theta) = C\xi' + \frac{||\theta||}{2}^2
    %\]
%when using inference algorithm $I$, that is $o^I(\theta)$ is the approximation of the primal

%objective given by $I$. To simplify exposure, we will drop the dependency on $\theta$.
In the following, we will use the notation of Section~\ref{bounds} and indicate
the choices of oracle $I$ with $Q$ for a chosen inference algorithm and $C$ for
using cached constraints.

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
        \toprule
                    & Average & Global \\
        \cmidrule{1-3}
    Unary terms only & 77.7& 83.2 \\
    Pairwise model (move making)& 79.6&84.6\\
    Pairwise model (exact)& 79.0 & 84.3\\
        \cmidrule{1-3}
    \citet{ladicky2009associative} & 75.8& 85.0\\
    \citet{gonfaus2010harmony} & 77&  75\\
    \citet{lucchi2013learning} & 78.9& 83.7\\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Accuracies on the MSRC-21 Dataset.  We compare a baseline model,
    our exact and approximately learned models and state-of-the-art
    approaches.\label{msrcacc}}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{caching}
\caption{%
Training time comparison using different caching heuristics.
Large dots correspond to $o^Q$, small dots correspond to $o^C$,
and the line shows $o_\W$. See the text for details.\label{caching}}
\end{figure*}
% much simpler model?

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lc}
        \toprule
                    & Jaccard \\
        \cmidrule{1-2}
    Unary terms only &  27.5 \\
    Pairwise model (move making)& 30.2\\
    Pairwise model (exact) & 30.4\\
        \cmidrule{1-2}
    \citet{dann2012pottics} & 27.4\\
    \citet{krahenbuhl2012efficient} & 30.2\\
    \citet{krahenbuhlparameter} & 30.8\\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Accuracies on the Pascal VOC Dataset. We compare our approach
    against approaches using the same unary potentials.\label{pascalacc}}

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ & 65.10 & 67.66  \\
    Estimated Objective $o^I$ &  67.62& 67.66\\
    True Primal Objective $o^E$& 69.92& 67.66\\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the MSRC-21 Dataset}
    \label{msrc_objective}
\end{table}

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ &92.06& 92.24\\
    Estimated Objective $o^I$ & 92.07 &92.24\\
    True Primal Objective $o^E$&92.35& 92.24  \\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the Pascal Dataset.}
    \label{pascal_objective}
\end{table}
